greta.Rmd

### 2019-07-11 notebook/ghost-fit.Rmd
high vs low inference

```{r}
data <- read_csv("../data/reps.csv")
data %>% ggplot(aes(t,x, group=reps)) + geom_line(alpha=0.1)
```

@@

@@

```{r}
x_t1 <- wide[-1,] # data$x[-1]
x_t <- wide[-n,] # data$x[-100]
dim(x_t)
dim(x_t1)
#tibble(x_t, x_t1) %>% ggplot(aes(x_t, x_t1)) + geom_point()
```

```{r}
#r <- 0.05 
Q <- 5
#sigma <- 0.02
#a <- 0.0233
K <- uniform(0, 10)
H <- uniform(0,  2)
a <- uniform(0, 1)
r <- uniform(0, 1)
#Q <- uniform(0, 10)
sigma <- uniform(0, 1)

# Model
mean <- x_t + r * x_t * (1 - x_t / K) - a * x_t ^ Q / (x_t ^ Q + H ^ Q)
distribution(x_t1) <- normal(mean, sigma)
m <- model(K, a, H, sigma, r)
```

@@

```{r}
#Q = 5
true <- data.frame(a = 0.023, r = .05, K = 2, H = .38, sigma = .02) %>%
  gather(variable, value)
```

@@

>>>>

```{r}
data <- read_csv("../data/reps.csv") # %>% filter(t %in% seq(0,4000, by=4))
data %>% ggplot(aes(t,x, group=reps)) + geom_line(alpha=0.02)
```

@@

## highs

@@

```{r}
x_t1 <- wide[-1,]
x_t <- wide[-n,] 
```

```{r}
r <- 0.05 
Q <- 5
K <- 2
# a <- 0.0233
H <- 0.38
sigma <- 0.02

# r <- uniform(0, 1)
# Q <- uniform(0, 10)
#K <- uniform(0, 10)
a <- uniform(0, 1)
# H <- uniform(0,  2)
#sigma <- uniform(0, 1)

# Model
mean <- x_t + r * x_t * (1 - x_t / K) - a * x_t ^ Q / (x_t ^ Q + H ^ Q)
distribution(x_t1) <- normal(mean, sigma)
m <- model(a)
```

@@

```{r}
#Q = 5
true <- 
  data.frame(a = 0.023 #, 
             #r = .05, 
             #K = 2, 
             #H = .38, 
             #sigma = .02
             ) %>%
  gather(variable, value)
```

@@

## lows

```{r}
wide <- data %>% 
  filter(reps %in% lows) %>%
  spread(reps, x) %>%
  select(-t) %>% 
  as.matrix()
n <- dim(wide)[1]

```{r}
x_t1 <- wide[-1,]
x_t <- wide[-n,] 
```

```{r}
mean <- x_t + r * x_t * (1 - x_t / K) - a * x_t ^ Q / (x_t ^ Q + H ^ Q)
distribution(x_t1) <- normal(mean, sigma)
m <- model(a)
```
